---
title: DANL Project
subtitle: "NYC Housing Prices"
author: 
  - Avery Fonda
  - Gordon Fagan
  - Kenzie Perkins

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---

```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Introduction

About this project :clap:

Our mission as AGK Real Estate is to figure out housing prices in NYC within different neighborhoods, and boroughs. This is relevant because we need to find the cost of housing to be able to make it more affordable for those living in NYC. The prices of homes today are on the rise, because of the pandemic and inflation and it is our mission to make it so everyone in NYC can have affordable living.

As a real estate agency it is our job to provide homes that our clients will love at a low price.

# Data

```{r}
nyc_housing_sales <- read_csv("https://bcdanl.github.io/data/nyc_housing_sales_2006-2023.csv")

print(nyc_housing_sales)
```

# What is the average housing price for each borough in NYC? (Kenzie)

```{r}
average_prices <- nyc_housing_sales |>
  group_by(borough) |>
  summarize(average_price =
              mean(sale_price, na.rm = TRUE))

```

```{r}
ggplot(data = average_prices) + 
  geom_col(mapping = 
               aes(x = borough, 
                   y = average_price),
             alpha = .5) + 
  facet_grid(borough ~ .)

```

# What month was the most popular in Queens for housing sales? (Avery)

```{r}
most_popular_month <- nyc_housing_sales %>%
  filter(borough == "Queens") %>%
  group_by(month) %>%
  summarize(total_sales = n()) %>%
  arrange(desc(total_sales)) %>%
  slice(1)

most_popular_month$month

```

Answer: August (8th month)

```{r}
most_popular_month <- nyc_housing_sales %>%
  filter(borough == "Queens") %>%
  group_by(month) %>%
  summarize(total_sales = n()) %>%
  arrange(desc(total_sales))

all_months <- unique(nyc_housing_sales$month)

all_months_sales <- merge(most_popular_month, data.frame(month = all_months), by = "month", all = TRUE)

ggplot(all_months_sales, aes(x = month, y = ifelse(is.na(total_sales), 0, total_sales))) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Monthly Housing Sales in Queens",
       x = "Month",
       y = "Total Sales")

ggplot(all_months_sales, aes(x = month, y = ifelse(is.na(total_sales), 0, total_sales))) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Monthly Housing Sales in Queens",
       x = "Month",
       y = "Total Sales") +
  scale_x_discrete(labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

```

# What is the average housing price for each neighborhood in the Queens borough? (Gordon)

```{r}

borough_name <- "Queens"
borough_data <- nyc_housing_sales %>%
  filter(borough == borough_name)

neighborhood_avg_price <- borough_data %>%
  group_by(neighborhood) %>%
  summarize(avg_price = mean(sale_price))

print(neighborhood_avg_price)

```

# Is there any correlation between square footage and housing prices in different NYC boroughs? (Kenzie)

```{r}
cor_data <- nyc_housing_sales |>
  filter(!is.na(gross_square_feet) & !is.na(sale_price)) |>
           group_by(borough) |>
                      summarize(corr = cor(gross_square_feet,
                                           sale_price))

```

```{r}
ggplot(cor_data, aes(x = borough, y = corr)) +
  geom_col() +
  labs(title = "Correlation: Square Footage vs Housing Prices",
       x = "Borough",
       y = "Correlation Coefficient") +
  theme_minimal()

```

# How many housing units were built in 1925? (Kenzie)

```{r}

units_1925 <- nyc_housing_sales |>
  filter(year_built == 1925) |>
           summarize(total_units_1925 =
                       sum(total_units, na.rm = TRUE))
print(units_1925)
```

# Which zipcode in NYC has the most housing? (Avery)

```{r}
nyc_housing_sales %>%
  group_by(zip_code) %>%
  count() %>%
  arrange(desc(n))

```

```{r}
nyc_housing_sales %>%
  group_by(zip_code) %>%
  count() %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = n, y = reorder(zip_code, n))) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Number of Housing Units by Zipcode in NYC",
       x = "Number of Housing Units",
       y = "Zipcode")

```

# What is the most expensive neighborhood to live in NYC? (Gordon)

```{r}

most_expensive_neighborhood <- nyc_housing_sales %>%
  filter(sale_price == max(sale_price))

most_expensive_neighborhood_name <- most_expensive_neighborhood$neighborhood[1]

print(paste("The most expensive neighborhood in NYC is:", most_expensive_neighborhood_name))

```

# What are the top 5 most expensive housing units in NYC? (Gordon)

```{r}

top_5_expensive_units <- nyc_housing_sales[order(-nyc_housing_sales$sale_price), ][1:5, ]

print(top_5_expensive_units)

```

# Which borough has the most apartments? (Avery)

```{r}
nyc_housing_sales %>%
  filter(building_class_category == "09 COOPS - WALKUP APARTMENTS") %>%
  group_by(borough) %>%
  count() %>%
  arrange(desc(n))

```

```{r}
nyc_housing_sales %>%
  filter(building_class_category == "09 COOPS - WALKUP APARTMENTS") %>%
  group_by(borough) %>%
  count() %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = borough, y = n)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Number of Apartments by Borough",
       x = "Borough",
       y = "Number of Apartments")

```

# Sources

https://www.nyc.gov/site/finance/property/glossary-property-sales.page

https://www.nyc.gov/assets/finance/jump/hlpbldgcode.html
